\newpage
\fancyhead[C]{Thomas Turner}
\section{Return to Safety} \label{Return to Safety}


\subsection{Introduction and Philosophy}
Traditionally \gls{RTH} is executed in commercial drone products in case of detected faults and errors. This is usually sufficient and convenient for the user. However, this specific use case provides cause to expand this functionality. In cases of partial thrust failure, provided it is not above the critical value needed to maintain stability, the \gls{UAV} will have to use less aggressive control in order to cause no further degeneration and compensate for lower actuator saturation levels. This makes the \gls{UAV} less robust to disturbances and therefore introduces a significant probability of crashing. Similarly, if the battery state of charge is depleting faster than predicted and hence causing a state of charge failure you can model this as a probability of failure at any given point given the unpredictability of degenerating cells \cite{cell stuff}. Lastly, if adverse weather conditions are detected causing instability, similarly to if there is partial thrust failure, the device can no longer be assumed to be robust to the environmental disturbances and has a significant probability of crashing. Given the difficulty of retrieval, this means that traditional \gls{RTH} is not the optimal strategy in these specific cases and instead a \gls{RTS} strategy is more appropriate.

\paragraph{When to use \gls{RTH}}
\gls{RTH} is always preferable to to \gls{RTS} as if you trace back the path you came down and return to the start location you can ensure that the path is obstacle free and you have returned to a safe and convenient location. Therefore, \gls{RTH} should be used when the probability of failure at any specific instant on the path is negligible as the drone is robust to the environmental conditions, and when the drone has accurate location sensing for avoidance of large obstacles and obstructions. This means in cases of redundant sensor or communication faults, non safety critical sensor faults, or if commanded by the base station, \gls{RTH} should be executed.

\paragraph{Objectives}
The objective of the \gls{RTS} system is to provide a robust and flexible procedure that can be operated from the flight controller with minimal added memory and time complexity that provides optimal or near optimal routes to safe landing zones. It should also be easy to setup and operate by untrained ground operators.


\input{Thomas/Return_To_Safety/1_Cost_Maps}
\input{Thomas/Return_To_Safety/2_Fault_Detection_And_Control}
\input{Thomas/Return_To_Safety/3_Path_Planning}

\input{Thomas/Return_To_Safety/4_Hardware_Deployement}
 